Working Notes

### 2019-02-25 notes.rmd
update

##Lit review:
	How to branch to Text Classification Primer, sub-pages look okay?
		Text_classifier_models	= 	Text Classification Primer
		Topic_categorization = Topic Categorization and Modeling Methods
		Choosing_classifier = Choosing a Text Classifier Method
		Classifier_comparison = Designing a Classifier Evaluation Workflow 
		Improving_classifier = Strategies for Improving Text Classifiers

@@

##Data Exploration:
	Help with aligning tables and keeping the NA values

##Findings:
	How to graph the different comparisons of NB values from different sources on same plot.

@@

##Etc.:
	Using a Bibliography in this format?
	Can menus have sub-pages?
	Adding automatic updates to top dates?
	Moving top dates?
	Fix GitHub auto-upload

>>>>

##Lit review:
	How to branch to Text Classification Primer
	  Use sub-menus
		Text_classifier_models	= 	Text Classification Primer
		Topic_categorization = Topic Categorization and Modeling Methods
		Choosing_classifier = Choosing a Text Classifier Method
		Classifier_comparison = Designing a Classifier Evaluation Workflow 
		Improving_classifier = Strategies for Improving Text Classifiers

@@

##Data Exploration:
	Help with aligning tables and keeping the NA values. 
	  Use full_join, not merge.

##Findings:
	How to graph the different comparisons of NB values from different sources on same plot? 
	  Add ggplot (data=) value.

@@

##Etc.:
	Using a Bibliography in this format?

	Can menus have sub-pages? 
	  Yep, using sub-pages
	Adding automatic updates to top dates? 
	  `r_sys.date()`
	Fix GitHub auto-upload
